---
title: "Lab 1: Introduction to Quarto"
author: "Oli Lane"
date: "9/26/2024"
format: html
editor: source
embed-resources: true
execute:
  echo: true
  error: true
---

# Part Two: Exploring Quarto Documents

## Specifying Global Execute Options

Execution options specify how the R code in your Quarto document should be displayed. This [guide](https://quarto.org/docs/computations/execution-options.html) provides descriptions on the options you can specify in a document's execution.

**Question 1** -- Add your name and the date to the YAML.

**Question 2** -- Add an `execute` line to your YAML that includes the following options, (1) your source code is always output on the page, and (2) your document will render even if there are errors.

## Running the Provided Code

```{r}
#| eval: false
#| echo: true
#| label: practicing-running-code

# Load a dataset into the R Environment.
data(ToothGrowth)

# Look at the summary of the variables in the dataset.
summary(ToothGrowth)
```

**Question 3** -- Let's spice this code up a bit. Delete `1 + 1` from the code chunk and paste in the code provided in the Lab 1 instructions.

### Tooth Growth Dataset

**Question 4** -- In your **console** (*not* in the Quarto document), type `?ToothGrowth` (or alternatively `help(ToothGrowth)`.Use the information that pops up in the *Help* pane in RStudio to fill in the blanks below.

*This dataset investigates the effect of Vitamin C on tooth growth in Guinea Pigs.*

*The two supplement delivery methods include OJ (orange juice) and VC (ascorbic acid).*

*`ToothGrowth` is a data frame with 60 **observations and*** 3 variables.

**Question 5** -- *Before* the code chunk, change the "Running the Provided Code" section header to a header that better describes the contents of this section (e.g., Tooth Growth Dataset).

## Creating a Plot

**Question 6** -- Replace the `plot(pressure)` code with the code provided in the Lab 1 instructions.

```{r}
#| echo: true
#| label: creating-a-plot
#| layout-ncol: 2
#| fig-align: "center"
#| fig-cap: 
#|   - "Length of Teeth vs Supplement"
#|   - "Length of Teeth vs Dose"

library(tidyverse)

ggplot(data = ToothGrowth, 
       mapping = aes(x = supp, y = len)) +
  geom_boxplot() +
  labs(x = "Supplement", y = "Length of Teeth (mm)")

ToothGrowth %>% 
  mutate(dose = as.factor(dose)) %>% 
  ggplot(mapping = aes(x = dose, y = len)) +
  geom_boxplot() +
  labs(x = "Dose of Supplement (mg/day)", y = "Length of Teeth (mm)")
```

Now, run this code chunk! You should see two side-by-side boxplots, one plot comparing tooth length between the two supplement delivery methods and one plot comparing tooth length between the three different dosages uses.

**Question 7** -- Read over the [Quarto documentation on figure options](https://quarto.org/docs/authoring/figures.html#computations) and add an option (`#|`) to the above code chunk to make the figures print side-by-side (i.e., in one row) in the rendered HTML file.

**Question 8** -- Specify in the code chunk options that these boxplots should be **center aligned**.

**Question 9** -- Specify a **figure caption** for the boxplots (using a code-chunk option).

**Question 10/11**

## Analyzing Vitamin C delivery methods

```{r}
#| echo: true

t.test(ToothGrowth$len ~ ToothGrowth$supp, var.equal = FALSE)


```

**Question 12**

1.  We fail to reject the null hypothesis because the p-value is 0.06, which is greater than most acceptable p-values, which are typically under 0.05.
2.  The provided confidence interval means that if we were to repeat the experiment many times, 95% of the time the difference in mean between the OJ and VC groups would fall between -0.17 and 7.57.

**Question 13**
section header created above t test code
